Exploring the ages of rotating stars using galactic dynamics: a novel approach to calibrating gyrochronology

### 2019-09-05 paper/discussion.tex
typo

For stars below the gap, in the 0.7-1.0 Gyr age range shown in figure
\ref{fig:age_cut}, velocity dispersion is relatively constant as a function of
temperature, however above the gap, in the 1.0-1.5 Gyr age range and older,
velocity dispersion increases with \teff.
The coolest stars in the 1.0-1.5 Gyr age range have the same velocity
dispersion as the mid-temperature stars in the age range above, and the
hottest stars in the age range above {\it that}, which indicates that the
period-\teff\ relations are {\it flat} at rotation periods between $sim$15-25
days, for 5500 K $<$ \teff\ $<$ 4000 K.
Below the gap, velocity dispersion within a given period range appears to {\it
decrease} with decreasing temperature.
The opposite appears to be true above the gap.

>>>>

For stars below the gap, in the 0.7-1.0 Gyr age range shown in figure
\ref{fig:age_cut}, velocity dispersion is relatively constant as a function of
temperature, however above the gap, in the 1.0-1.5 Gyr age range and older,
velocity dispersion increases with \teff.
The coolest stars in the 1.0-1.5 Gyr age range have the same velocity
dispersion as the mid-temperature stars in the age range above, and the
hottest stars in the age range above {\it that}, which indicates that the
period-\teff\ relations are {\it flat} at rotation periods between $\sim$15-25
days, for 5500 K $<$ \teff\ $<$ 4000 K.
Below the gap, velocity dispersion within a given period range appears to {\it
decrease} with decreasing temperature.
The opposite appears to be true above the gap.
